\normalfont\spacedallcaps{Hazardous asteroids forecast via Markov random fields}

### 2021-11-19 Manuscript/manuscript.tex
PUB

\begin{equation}
\dot{\textbf{r}}=\dot{r}\hat{\textbf{r}}+r\dot{\theta}\hat{\boldsymbol{\theta}}
\end{equation}

@@

If we consider the motion of the body $m_{2}$ in the time interval $\delta t$ we have that the area $\delta A$ illustrated in Fig will be \cite{murray1999solar}:

@@

where the Taylor expansion at first order was used. Therfore

@@

but we know that $h$ is constant, therefore the first derivative, is constant. This is the $2^{th}$ Kepler law

\begin{figure}[h]
\begin{center}
\includegraphics[width=1\textwidth]{Figures/Area_dynamics.png}
\caption{The portion of area $\delta A$ obtained when the position vector moves with an angle $\delta\theta$. Image taken from \cite{murray1999solar}}
\label{RF_Importance}
\end{center}
\end{figure}

>>>>

\begin{equation}
\dot{\textbf{r}}=\dot{r}\hat{\textbf{r}}+r\dot{\theta}\hat{\boldsymbol{\theta}}
\label{eq_dyn_nop}
\end{equation}

@@

If we consider the motion of the body $m_{2}$ in the time interval $\delta t$ we have that the area $\delta A$ illustrated in Fig \ref{Area_dynamics} will be \cite{murray1999solar}:

@@

where the Taylor expansion at first order was used. Therfore  \cite{murray1999solar}:

@@

but we know that $h$ is constant, therefore the first derivative, is constant. This is the $2^{th}$ Kepler law. The Eq. \ref{eq_dyn_nop} in polar coordinates  \cite{murray1999solar}:

\begin{equation}
\ddot{r}-r\dot{\theta}^{2}=-\frac{\mu}{r^{2}}
\end{equation}

This differential equation can be rewritten as an armonic oscillator with the  substitutions $u=\dfrac{1}{r}$ $h=r^{2}\dot{\theta}$ \cite{murray1999solar}:

\begin{equation}
\dot{r}=-\frac{1}{u}\dfrac{du}{d\theta}\dot{\theta}=-h\frac{du}{d\theta}
\end{equation}

\begin{equation}
\ddot{r}=-h\dfrac{d^{2}u}{d\theta^{2}}\dot{\theta}=-h^{2}u^{2}\frac{d^{2}u}{d\theta^{2}}
\end{equation}

\begin{equation}
\dfrac{d^{2}u}{d\theta^{2}}+u=\frac{\mu}{h^{2}}
\end{equation}

\begin{equation}
u=\frac{\mu}{h^{2}}\left[1+e\cos(\theta-\phi\right]
\end{equation}

where the integration constants e and $\phi$ are respectively the amplitude and the phase. Therefore we have \cite{murray1999solar}:

\begin{equation}
r=\dfrac{p}{1+e\cos(\theta-\phi}
\end{equation}

In this form we can recognize in e the eccentricity and p is the semilatus rectum \cite{murray1999solar}:

\begin{equation}
p=\frac{h^{2}}{\mu}
\end{equation}

Depening on the eccentricity we have four possibile conics

\begin{itemize}
\item circle:  e=0 \quad $p=a$
\item ellipse: 0<e<1 \quad $p=a$
\item parabola: e=1 \quad $p=2q$
\item hyperbola: e>1 \quad $p=a(e^{2}-1)$
\end{itemize}

in which a is the semi-major axis of the conic. The shape of these orbits is reported in Fig. \ref{Conics}.

\begin{figure}[h]
\begin{center}
\includegraphics[width=1\textwidth]{Figures/Area_dynamics.png}
\caption{The portion of area $\delta A$ obtained when the position vector moves with an angle $\delta\theta$. Image taken from \cite{murray1999solar}}
\label{Area_dynamics}
\end{center}
\end{figure}

\begin{figure}[h]
\begin{center}
\includegraphics[width=1\textwidth]{Figures/Conics.png}
\caption{The four possible orbits as obtained from a sectionof a cone. Image taken from \cite{murray1999solar}}
\label{Conics}
\end{center}
\end{figure}
